---
title: "Bootstrap the Gompertz Curve"
date: "Generated: `r Sys.Date()`"
runtime: shiny
output:
    html_document:
        toc: true
        toc_depth: 2
        theme: spacelab
        highlight: zenburn
        number_sections: false
---

```{r global_opts, include=FALSE}

knitr::opts_chunk$set(fig.path="Figs/", echo=FALSE, warning=FALSE,
                      message=FALSE, dev='svg')

```


-------

# Info
* [code](https://github.com/nverno/allometry)

Gompterz model is fit for __1998 ABBA__ only, using __residual elevation__ (from linear model `ELEV ~ canopy98`, shown below).  Only live trees with non-missing height and dbh are included.  The model is seeded on each iteration with the parameters reported in the manuscript.  The bootstrapping is done with different sampling schemes (to determine dependence of model on size bias):

    - all the data weighted equally
	- split the data by DBH size and draw equal sized samples from each size class

The gompertz model:
$$
\alpha = a + a_1 \textrm{elev_r} + a_2 \textrm{canht} + a_3 \textrm{elev_r*canht} \\
\beta = b + b_1 \textrm{elev_r} + b_2 \textrm{canht} + b_3 \textrm{elev_r*canht} \\
\beta e^{log(\frac{\gamma}{\beta}) e ^{-\alpha \ \textrm{dbh}}}
$$


```{r setup}
library(ggplot2)
library(MASS)
library(reshape2)
library(dplyr)
source("~/work/allometry/gompertz/setup.R", chdir=T)
params <- reactiveValues()
params[["seed"]] <- ps

```

------

# Choose Model Parameters

## Canopy/Residual Elevation

Canopy height calculation and residual elevation:
```{r resid_elev}

checkboxInput("excludeTarg", "Exclude Target")
checkboxInput("ratio", "Log Relative Canopy Height (log(target / estimate))")
checkboxInput("logElev", "Log Elevation")
getCanopy <- reactive({ 
    canht <- ifelse(input$excludeTarg, "cht_notarget98", "cht98")
    print(canht)
    if (input$ratio) {
        lcan <- ifelse(pp[,canht] > 0, log(pp[, canht]), 0)
        log(pp[, "HTTCR98"]) - lcan
    } else
        pp[, canht]
})
getElev <- reactive({
    if (input$logElev)
        log(pp[,"ELEV"])
    else
        pp[,"ELEV"]
})
getResFit <- reactive({ 
    elev <- getElev()
    canht <- getCanopy()
    lm(elev ~ canht)
})
getData <- reactive({
    fit <- getResFit()
    pp$relev <- residuals(fit)
    pp$canht <- getCanopy()
    pp$elev <- getElev()
    pp
})

renderPlot({
    xlab <- ifelse(input$ratio, "Log(Height/Canopy Height)", "Canopy Height")
    ylab <- ifelse(input$logElev, "Log Elevation", "Elevation")
    dat <- getData()
    fit <- getResFit()
    par(mfrow = c(1,2))
    scatter.smooth(dat[,"canht"], dat[,"elev"], lpars = list(col="azure3", lty=2),
                   xlab=xlab, ylab=ylab)
    legend("topright", c("Fit", "Trend"), col=c("red", "azure3"), lty=c(1, 2))
    abline(fit, col="red")
    scatter.smooth(predict(fit), dat[,"relev"], lpars = list(col="azure3", lty=2),
                   xlab="Predicted", ylab=paste("Residual", ylab, ", Obs-Pred"))
    abline(h=0, lty=2)
})

renderPrint({
    cat("Model Summary\n")
    fit <- getResFit()
    print(summary(fit))
})

```

-------

# Initialize Model
Compute seed parameter estimates (using defined residual variable) for model with no size classes.  These parameters will then be used as the starting parameters for each bootstrap run, and the base parameters to which models with size classes will be compared.

```{r init_params}
shinyUI(fluidPage(
    fluidRow(
        column(3, actionButton("initPS", "Initialize")),
        column(6, checkboxInput("useMSpars", "Start from manuscript parameters", value=T))
    )
))

psName <- reactive({
    ids <- c("ps")
    if (input$excludeTarg) ids <- c(ids, "notarget")
    if (input$ratio) ids <- c(ids, "logratio")
    if (input$logElev) ids <- c(ids, "logElev")
    paste0(paste(ids, collapse="_"), ".rds")
})

renderPrint({
    if (input$initPS) {
        fname <- psName()
        sprintf("Initialized and saved as %s.", fname)
    }
    else "Not Initialized"
})

initPS <- reactive({
    if (input$initPS) {
        dat <- getData()
        fname <- psName()
        if (input$useMSpars) ps <- paper_ps
        res <- run_boot(dat, inds=list(1:nrow(dat)), ps=ps, reps=10, update=T)
        pars <- as.list(colMeans(res))
        params[["seed"]] <- pars
        saveRDS(params[["seed"]], paste0("~/work/allometry/gompertz/temp/", fname))
        params
    } else "Not Initialized"
})

renderTable({ 
    input$initPS
    pars <- isolate(initPS())
    if (is.list(pars))
        as.data.frame(params[["seed"]])
    else c()
}, digits=4)

renderPlot({
    if (input$initPS) {
        dat <- getData()
        pars <- params[["seed"]]
        preds <- do.call(gompertz, list(pars, dat[,"DBH98"], dat[,"relev"], dat[,"canht"]))
        rmse <- sqrt( mean( (preds - dat[,"HTTCR98"])^2 ) )
        plot(HTTCR98 ~ DBH98, data=dat)
        points(dat$DBH98, preds, col="azure3")
        legend("topleft", c(paste("RMSE:", round(rmse, 3))))
    }
})

```

-------

## Size Classes

Select size classes to sample evenly.  The bootstrap will (this is adjustable below) by default sample the same number of points as the original sample (with replacement, n = `r nrow(pp)`) regardless of size class selection.  There will be three bootstraps run, one of which will sample the data without size classes (equal weighting to all data).  The size classes for the other two runs are selected below.

```{r size_classes, cache=F}

classes1 <- reactive({ seq(-0.01, max(pp$DBH98)+0.1, len=input$numBreaks1 + 1) })
classes2 <- reactive({ seq(-0.01, max(pp$DBH98)+0.1, len=input$numBreaks2 + 1) })

sizePlot <- renderPlot({
    dat <- getData()
    plot(HTTCR98 ~ DBH98, data=dat)
    abline(v = classes1(), col="green", lwd=2)
    abline(v = classes2(), col="orange", lwd=2, lty=2)
    legend("topright", c("run 1", "run 2"), col=c("green", "orange"), lty=c(1,2))
})

sizeHist <- renderPlot({
    dat <- getData()
    cl1 <- classes1()
    cl2 <- classes2()
    q1 <- cut(dat[,"DBH98"], breaks=cl1)
    inds1 <- lapply(names(table(q1)), function(x) which(q1 == x))
    run1 <- unlist(lapply(inds1, function(i) sample(i, ceiling(nrow(dat)/input$numBreaks1), rep=T)))
    q2 <- cut(dat[,"DBH98"], breaks=cl2)
    inds2 <- lapply(names(table(q2)), function(x) which(q2 == x))
    run2 <- unlist(lapply(inds2, function(i) sample(i, ceiling(nrow(dat)/input$numBreaks2), rep=T)))
    samp <- data.frame(dbh=c(dat[,"DBH98"], dat[run1,"DBH98"], dat[run2,"DBH98"]),
                       run=factor(rep(c(0,1,2), times=c(nrow(dat), length(run1), length(run2)))))

    if (input$sizeOverlay) 
        ggplot(samp, aes(dbh, group=run, fill=run)) + geom_density(alpha=0.5)
    else 
        ggplot(samp[samp$run == input$sizeRun,], aes(dbh)) + geom_histogram()
})

shinyUI(fluidPage(
    titlePanel("Select size classes"),
    helpText("Choose sizes classes for both bootstrap runs."),
    sidebarLayout(
        sidebarPanel(
            numericInput("numBreaks1", "First Run", min=2, max=10, value=4),
            numericInput("numBreaks2", "Second Run", min=2, max=10, value=3),
            conditionalPanel(
                condition = "input.sizeTabs == 'Histogram'",
                radioButtons("sizeRun", "Choose run:", choices=c(0, 1, 2), selected=0, inline=FALSE),
                checkboxInput("sizeOverlay", "Overlay densities")
            )
            
        ),
        mainPanel(
            tabsetPanel(
                id = "sizeTabs",
                tabPanel("Scatter", sizePlot),
                tabPanel("Histogram", sizeHist)
            )
        )
    )
))

```

-------

# Bootstrap
Run the bootstrap

**TODO**: add programmable input to define test statistic function for bootstrap

```{r bootstrap}
shinyUI(fluidPage(
    titlePanel("Bootstrap parameters"),
    fluidRow(
        column(6, sliderInput("R", "Number of bootstraps", min=1, max=1000, value=5)),
        column(6, sliderInput("n", "Number samples", min=1, max=2000, value=500))
    ),
    fluidRow(
        column(6, checkboxInput("updatePS", "Update Parameters on each bootstrap")),
        column(6, checkboxInput("nPerClass", "Use as number of samples/size class"))
    )
))
```

## Compare specific runs

```{r}

actionButton("run", "Run it!")
results <- reactive({
    if (input$run) {
        dat <- getData()  # variables 'elev' and 'canht'
        reps <- input$R
        cl1 <- classes1()
        cl2 <- classes2()
        updatePS <- input$updatePS
        nPerClass <- input$nPerClass
        ps <- params$seed
        
        ## Run 0: sample data equally
        cat("\nRun 0\n")
        inds0 <- list(a=1:input$n)
        res0 <- run_boot(dat=dat, inds=inds0, n=input$n, ps=ps, reps=reps, update=updatePS,
                         nPerClass = nPerClass)

        ## Run 1
        dat$qs1 <- cut(dat[,"DBH98"], breaks=cl1)
        inds1 <- lapply(names(table(dat$qs1)), function(x) which(dat$qs1 == x))
        res1 <- run_boot(dat=dat, inds=inds1, n=input$n, ps=ps, reps=reps, update=updatePS,
                         nPerClass = nPerClass)
        
        ## Run 2
        dat$qs2 <- cut(dat[,"DBH98"], breaks=cl2)
        inds2 <- lapply(names(table(dat$qs2)), function(x) which(dat$qs2 == x))
        res2 <- run_boot(dat=dat, inds=inds2, n=input$n, ps=ps, reps=reps, update=updatePS,
                         nPerClass = nPerClass)
        
        list(run0=res0, run1=res1, run2=res2)
    }
    else "Not Run"
})

## Reactives to result
getStats <- reactive({
    input$run
    res <- isolate(results())
    
    if (is.list(res)) {
        runs <- res[paste0("run", input$runs)]
        ests <- do.call(cbind, lapply(runs, function(r) matrix(colMeans(r))))
        stdErr <- do.call(cbind, lapply(runs, function(r) matrix(sqrt(diag(cov(r))))))
        bias <- do.call(cbind, lapply(runs, function(r) matrix(colMeans(r - colMeans(r)))))
        coefv <- 100 * (stdErr / ests)
        out <- do.call(cbind, list(ests=ests, stdErr=stdErr, bias=bias, coefv=coefv))
        colnames(out) <- paste0(rep(names(runs), times=4), ":",
                                rep(c("estimate", "stdErr", "bias", "coefv"), each=length(names(runs))))
        rownames(out) <- names(ps)
        as.data.frame(out)
    } else NULL
})

## Render result
summCoefs <- renderTable({
    input$run
    res <- isolate(results())
    if (is.list(res)) {
        runs <- res[input$runs]
        run <- runs[paste0("run", input$summRun)]
        print(summary(run))
    } else table(c())
})

plotResults <- renderPlot({
    input$run
    dat <- getData()
    res <- isolate(results())
    if (is.list(res))
        plot(HTTCR98 ~ DBH98, data=dat)
    else plot(0, 0, type="n")
})

statsCoefs <- renderTable({
    input$run
    res <- isolate(results())
    if (is.list(res)) {
        stats <- getStats()
        stats[,grep(paste(input$displayStats, collapse = "|"), names(stats))]
    } else table(c())
})

coefHist <- renderPlot({
    input$run
    res <- isolate(results())
    if (is.list(res)) {
        vals <- lapply(res, function(x) x[,colnames(x) == input$histPar])
        dat <- data.frame(vals=unlist(vals), run=rep(names(vals), each=length(vals[[1]])))
        ggplot(dat, aes(vals, col=run, fill=run, group=run)) + geom_density(alpha=0.3)
    }
})

shinyUI(fluidPage(
    titlePanel("Bootstrap Results"),
    sidebarLayout(
        sidebarPanel(
            checkboxGroupInput("runs", "Show results for runs:", choices=c(0,1,2), selected=c(0,1,2),
                               inline=T),
            conditionalPanel(
                condition = "input.resultTabs == 'Statistics'",
                checkboxGroupInput("displayStats", "Show:", 
                                   choices=c("estimate", "stdErr", "bias", "coefv"), 
                                   selected=c("estimate", "stdErr"))
            ),
            conditionalPanel(
                condition = "input.resultTabs == 'Histogram'",
                radioButtons("histPar", "Paramater:", choices=names(ps), selected="a", inline=TRUE)
            ),
            conditionalPanel(
                condition = "input.resultTabs == 'Coefficients'",
                radioButtons("summRun", "Run:", choices=c(0,1,2), selected=1, inline=FALSE)
            )
        ),
        
        mainPanel(
            tabsetPanel(
                id = "resultTabs",
                tabPanel("Coefficients", summCoefs),
                tabPanel("Plot", plotResults),
                tabPanel("Statistics", statsCoefs),
                tabPanel("Histogram", coefHist)
            )
        )
    )
))

renderPrint({
    input$run
    
    res <- isolate(results())
    if (is.list(res)) {
        cl1 <- classes1()
        cl2 <- classes2()
        cat("Equal Weightings:\n")
        print(summary(res[[1]]))
        
        cat(paste("\nRun 1: breaks= [", paste(cl1, collapse=", "), "]\n"))
        print(summary(res[[2]]))
        
        cat(paste("\nRun 2: breaks= [", paste(cl2, collapse=", "), "]\n"))
        print(summary(res[[3]]))
    } else print(res)
})

```

----------

## Sensitivity to Binning
Bootstrap across wide range of size class (this may take some time).

```{r boot_sense}

shinyUI(fluidPage(
    titlePanel("Sensitivity Parameters"),
    fluidRow(
        column(6, sliderInput("numSizes", "Number of size classes:", min=0, max=100, value=2))
        ## column(6, sliderInput("repsPerClass", "#bootstraps per class", min=1, max=10, value=3))
    )
))
actionButton("run_sense", "Run sensitivity test")

getRMSE <- function(coefs) {
}

## Reactive values
senseResults <- reactive({
    if (input$run_sense) {
        dat <- getData()
        reps <- input$R
        bins <- input$numSizes
        ps <- params$seed

        res <- lapply(1:bins, function(i) {
            dat$qs <- cut(dat[, "DBH98"], breaks=seq(-0.01, max(dat[, "DBH98"])+0.1,
                                              len=i+1))
            inds <- lapply(names(table(dat$qs)), function(x) which(dat$qs == x))
            run_boot(dat=dat, inds=inds, n=input$n, ps=ps, reps=reps)
        })
        
        ## Root mean squares
        rmses <- lapply(res, function(x) {
            sapply(1:nrow(x), function(y) {
                pars <- as.list(x[y, ])
                preds <- do.call(gompertz, list(pars, dat[,"DBH98"], dat[,"relev"], dat[,"canht"]))
                rmse <- sqrt( mean( (preds - dat[,"HTTCR98"])^2 ) )
            })
        })

        res <- melt(do.call(rbind, res), varnames=c("bins", "coef"))
        res$bins <- as.factor(rep(rep(1:bins, each=reps+1), times=length(names(table(res$coef)))))
        res$run <- as.factor(rep(rep(1:(reps+1), times=length(names(table(res$coef)))), times=bins))
        attr(res, "rmse") <- do.call(c, rmses)
        attr(res, "bin") <- as.factor(rep(1:bins, each=reps+1))
        attr(res, "run") <- as.factor(rep(1:(reps+1), times=bins))
        res
    } else "Not Run"
})

renderPrint({
    input$run_sense
    res <- isolate(senseResults())
    if (is.list(res)) {
        sprintf("Ran with %s size classes, %s bootstraps, each bootstrap with %s samples",
                input$numSizes, input$R, input$n)
    } else "Not Run"
})

## Output
traceCoefs <- renderPlot({
    input$run_sense
    res <- isolate(senseResults())
    if (is.list(res)) {
        ests <- res %>% filter(run != 1) %>%
          group_by(bins, coef) %>% summarise(estimate=mean(value))
        if (input$traceType == "Scatter") pars <- input$tracePars
        else pars <- input$traceVar
        res <- res[res$coef %in% pars & res$run != 1,]
        
        if (input$traceType == "Scatter") {
            p <- ggplot(res, aes(bins, value, group=coef, color=coef)) +
              theme_bw() + xlab("Number of Size Bins") + ylab("Value")
            if (input$tracePoints)
                p <- p + geom_point(alpha=.4, size=3, position=position_jitter(width=0.05))
            if (input$traceCurve)
                p <- p + geom_smooth(fill=NA)
            if (input$traceError)
                p <- p + stat_summary(fun.y=mean, geom="point", fill="black", pch=21, size=3) + 
                  stat_summary(fun.data=mean_cl_normal, geom="errorbar", color="black",
                               width=0.03, alpha=0.7, conf.int=input$traceConf)
            if (input$traceLine)
                p <- p + geom_path(data=ests[ests$coef %in% pars,], 
                                   aes(bins, estimate, group=coef, color=coef), lwd=1.3, lty=2)
        } else if (input$traceType == "Boxplot")
              p <- ggplot(res, aes(bins, value, group=bins)) +
                geom_boxplot() + theme_bw()
        p
    }
})

traceRMSE <- renderPlot({
    input$run_sense
    res <- isolate(senseResults())
    if (is.list(res)) {
        dat <- data.frame(bin=attr(res, "bin"), rmse=attr(res, "rmse"), run=attr(res, "run"))
        dat <- dat[dat$run != 1, ]
        if (input$rmseType == "Scatter")
            ggplot(dat, aes(bin, rmse)) + geom_point(alpha=0.4, size=3, position=position_jitter(width=0.05)) +
              ggtitle("RMSE by Number of Size Classes") + theme_bw() +
              stat_summary(fun.y=mean, geom="point", fill="black", pch=21, size=3) +
              stat_summary(fun.data=mean_cl_normal, geom="errorbar", color="black", width=0.25, 
                           alpha=0.7, conf.int=0.95)
        else if (input$rmseType == "Boxplot")
            ggplot(dat, aes(bin, rmse, group=bin)) + geom_boxplot() + theme_bw()
    }
})

traceAlphaBeta <- renderPlot({
    input$run_sense
    res <- isolate(senseResults())
    if (is.list(res)) {
        dat <- getData()
        if (input$abType == 'Scatter') vs <- input$abVars
        else vs <- input$abBoxVar
        elev <- input$elevAB
        canht <- input$canhtAB
        
        AB <- dcast(res, bins + run ~ coef)
        alpha <- AB$a + AB$a1*elev + AB$a2*canht + AB$a3*elev*canht
        beta <- AB$b + AB$b1*elev + AB$b2*canht + AB$b3*elev*canht
        samp <- melt(data.frame(run=attr(res, "run"), bin=attr(res, "bin"), alpha=alpha, beta=beta))
        baseAlpha <- samp[samp$variable=="alpha" & samp$run==1 & samp$bin==1, "value"]
        baseBeta <- samp[samp$variable=="beta" & samp$run==1 & samp$bin==1, "value"]
        samp <- samp[samp$run != 1 & samp$variable %in% vs, ]

        if (input$abType == "Scatter")
            p <- ggplot(samp, aes(bin, value, group=variable, color=variable)) + 
              geom_point(alpha=0.4, size=3) + theme_bw() +
              stat_summary(fun.y=mean, geom="point", fill="black", pch=21, size=3) +
              stat_summary(fun.data=mean_cl_normal, geom="errorbar", color="black", width=0.25, 
                           alpha=0.7, conf.int=0.95)
        else if (input$abType == "Boxplot")
            p <- ggplot(samp, aes(bin, value, group=bin)) +
              geom_boxplot() + theme_bw()

        if (input$abBase) {
            if ("beta" %in% vs)
                p <- p + geom_hline(data=data.frame(base=baseBeta), aes(yintercept=base), lty=2)
            if ("alpha" %in% vs)
                p <- p + geom_hline(data=data.frame(base=baseAlpha), aes(yintercept=base), lty=2)
        }
        p
    }
})

panel.cor <- function(x, y, digits = 2, cex.cor, ...)
{
    usr <- par("usr"); on.exit(par(usr))
    par(usr = c(0, 1, 0, 1))
    ## correlation coefficient
    r <- cor(x, y)
    txt <- format(c(r, 0.123456789), digits = digits)[1]
    txt <- paste("r= ", txt, sep = "")
    text(0.5, 0.6, txt)
    
    ## p-value calculation
    p <- cor.test(x, y)$p.value
    txt2 <- format(c(p, 0.123456789), digits = digits)[1]
    txt2 <- paste("p= ", txt2, sep = "")
    if(p<0.01) txt2 <- paste("p= ", "<0.01", sep = "")
    text(0.5, 0.4, txt2)
}

traceCorr <- renderPlot({
    input$run_sense
    res <- isolate(senseResults())
    if (is.list(res)) {
        vs <- input$corrVars
        AB <- dcast(res, bins + run ~ coef)
        pairs(AB[,vs], upper.panel=panel.cor)
    }
})

abVars <- renderUI({
    dat <- getData()
    list(
        helpText("Fix values of elevation and canopy height."),
        numericInput("elevAB", "Elevation:", min(round(min(dat$relev), 2)),
                     max=round(max(dat$relev), 2), value=mean(dat$relev)),
        ## sliderInput("elevAB", "Elevation:", min=round(min(dat$relev),2), max=round(max(dat$relev),2), 
        ##             value=mean(dat$relev)),
        numericInput("canhtAB", "Canopy Height:", min(round(min(dat$canht), 2)),
                     max=round(max(dat$canht), 2), value=mean(dat$canht)),
        ## sliderInput("canhtAB", "Canopy Height:", min=round(min(dat$canht),2), 
        ##             max=round(max(dat$canht), 2), value=mean(dat$canht)),
        conditionalPanel(
            condition = "input.abType == 'Scatter'",
            checkboxGroupInput("abVars", "Show:", choices=c("alpha", "beta"), selected=c("alpha", "beta"), inline=TRUE)
        ),
        conditionalPanel(
            condition = "input.abType == 'Boxplot'",
            radioButtons("abBoxVar", "Show:", choices=c("alpha", "beta"), selected="alpha", inline=TRUE)
	),
        checkboxInput("abBase", "Show baseline alpha-beta")
    )
})

shinyUI(fluidPage(
    titlePanel("Size Class Sensitivity"),
    sidebarLayout(
        sidebarPanel(
            conditionalPanel(
                condition = "input.senseTabs == 'Coefficients'",
                radioButtons("traceType", "Graph Type:", choices=c("Scatter", "Boxplot"), 
                             selected="Scatter", inline=TRUE),
                conditionalPanel(
                    condition = "input.traceType == 'Scatter'",
                    checkboxGroupInput("tracePars", "Trace parameters:", names(ps), selected=c(),
                                       inline=T),
                    checkboxInput("tracePoints", "Show Points", value=T),
                    checkboxInput("traceCurve", "Add spline", value=T),
                    checkboxInput("traceLine", "Line", value=T),
                    checkboxInput("traceError", "Standard errors", value=T),
                    conditionalPanel(
                        condition = "input.traceError == true",
                        helpText("Default set to 1 se (0.682 normal conf.)"),
                        sliderInput("traceConf", "Conf. level", min=0.5, max=.99, value=0.682)
                    )
                ),
                conditionalPanel(
                    condition = "input.traceType == 'Boxplot'",
                    radioButtons("traceVar", "Parameter:", choices=names(ps), selected=NULL, inline=TRUE)
                    
                )
            ),
            conditionalPanel(
                condition = "input.senseTabs == 'RMSE'",
                radioButtons("rmseType", "Graph Type:", choices=c("Scatter", "Boxplot"), 
                             selected="Scatter", inline=TRUE)
            ),
            conditionalPanel(
                condition = "input.senseTabs == 'AlphaBeta'",
                radioButtons("abType", "Graph Type:", choices=c("Scatter", "Boxplot"), 
                             selected="Scatter", inline=TRUE),
                abVars
            ),
            conditionalPanel(
                condition = "input.senseTabs == 'Correlations'",
                checkboxGroupInput("corrVars", "Parameters:", choices=names(ps), selected=c("a", "b"))
            )
        ),
        
        mainPanel(
            tabsetPanel(
                id = "senseTabs",
                tabPanel("Coefficients", traceCoefs),
                tabPanel("RMSE", traceRMSE),
                tabPanel("AlphaBeta", traceAlphaBeta),
                tabPanel("Correlations", traceCorr)
            )
        )
    )
))

shinyUI(downloadButton("saveSenseResults", "Save Sensitivity Results"))
saveRes <- downloadHandler(
    filename = function() { 
        paste0("~/work/allometry/gompertz/temp/sense_cl", input$numSizes, "_boot", input$R,
           "_n", input$n, ".rds")
    },
    content = function(file) {
        res <- isolate(senseResults())
        saveRDS(res, file)
    }
)


```
